\documentclass[10pt,a4paper,ragged2e]{cv}

% Page layout
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\usepackage{hyperref}

% Font
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Colours
\definecolor{Blue}{HTML}{3e70bb}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
% \colorlet{heading}{Blue}
\colorlet{accent}{Blue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Itimize & Ratings
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Kris Foster}
\tagline{Software Engineer}

\personalinfo{
  \email{krisfoster@live.ie}
  \phone{+353 877836033}
  \location{Dublin, Ireland}
  \linkedin{\href{https://www.linkedin.com/in/kriscfoster/}{linkedin.com/in/kriscfoster}}
  \github{\href{https://github.com/kriscfoster/}{github.com/kriscfoster}}
%  \homepage{krisfoster.com}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

\cvsection[right-sidebar]{Experience}
\cvevent{Senior Software Engineer}{Salesforce}{August 2020 -- Present}{Dublin, Ireland}
\begin{itemize}
\item Software Engineer SMTS (Senior Member of Technical Staff) with the Production Engineering Tools Team.
\item Using Spring, Kotlin \& Node.js to build web applications in the cloud with Spinnaker, Terraform, Kubernetes \& AWS.
\end{itemize}

\divider

\cvevent{Software Engineer}{Salesforce}{May 2019 -- July 2020}{Dublin, Ireland}
\begin{itemize}
\item Software Engineer MTS (Member of Technical Staff) with the Production Engineering Tools Team.
\item Building web applications using Java, Kotlin, Spring, Node.js \& React.js. Working in the cloud with AWS \& Kubernetes.
\end{itemize}

\divider

\cvevent{Intern \& Associate Software Engineer}{Salesforce}{June 2017 -- April 2019}{Dublin, Ireland}
\begin{itemize}
\item Joined the Production Engineering Tools team as an intern.
\item Continued to work part-time until studies were finished, then joined as a Software Engineer AMTS (Associate Member of Technical Staff).
\item Worked on the Refocus Rooms project (Incident Management Console used by Site Reliability).
\item Full stack JavaScript with Node.js \& React.js.
\end{itemize}

\cvsection{Education}
\cvevent{University College Dublin (UCD)}{M.Sc Advanced Software Engineering}{ 2020 -- 2022}{Dublin, Ireland}
Part-time Masters in Advanced Software Engineering.

\divider

\cvevent{University College Dublin (UCD)}{B.Sc Computer Science}{ 2014 -- 2018}{Dublin, Ireland}
\item Graduated with a 2.1 degree.

\cvsection{Certifications}
\begin{itemize}
\item AWS Certified Solutions Architect - Associate (2019).
\item CKAD: Certified Kubernetes Application Developer (2020).
\item HashiCorp Certified Terraform Associate (2020).
\end{itemize}

\clearpage

% \cvsection[page2sidebar]{Publications}

\nocite{*}

\end{document}
