\cvsection{TECHNICAL SKILLS}
\cvtag{Java}
\cvtag{Kotlin}
\cvtag{JavaScript}
\cvtag{Node.js}
\cvtag{React.js}
\cvtag{Spring}
\cvtag{Git}
\cvtag{Heroku}
\cvtag{Docker}
\cvtag{Kubernetes}
\cvtag{MongoDB}
\cvtag{PostgreSQL}
\cvtag{aws}
\cvtag{Terraform}

% \cvachievement{\faTrophy}{}{Something}
% \divider\smallskip

\cvsection{Projects}
\cvproject{Leinster Table Tennis Website}
\begin{itemize}
\item \href{https://leinstertt.com}{leinstertt.com}
\item Built for the Leinster Table Tennis Association \& hosted on GitHub pages.
\item Developed using HTML, CSS, JavaScript \& Bootstrap.
\end{itemize}

\smallskip

\cvproject{Pictionary Word Generator}
\begin{itemize}
\item \href{https://pictionary-banter.herokuapp.com/}{pictionary-banter.herokuapp.com}
\item Side project used for some family games during Christmas.
\item Developed using Kotlin, Spring, Thymeleaf \& Bootstrap.
\item Deployed on Heroku.
\end{itemize}

\smallskip

\cvproject{Currency Converter}
\begin{itemize}
\item \href{https://currency-converter-project.herokuapp.com/}{currency-converter-project.herokuapp.com}
\item Side project built to get familiar with some Spring Boot concepts.
\item Developed using Java, Spring, Thymeleaf \& Bootstrap.
\item Deployed on Heroku.
\end{itemize}

\smallskip

\cvproject{Sorting Algorithm Visualiser}
\begin{itemize}
\item \href{https://kriscfoster.github.io/sorting-algorithm-visualiser/}{kriscfoster.github.io/sorting-algorithm-visualiser}
\item Side project built to get familiar with some sorting algorithms.
\item Developed using HTML, CSS \& vanilla JavaScript.
\item Hosted on GitHub pages.
\end{itemize}

\cvsection{Hobbies}
\begin{itemize}
\item 4x Dublin Marathon Finisher (2020, 2018, 2016, 2014).
\item Creating Software Development tutorials.

\end{itemize}
